### 2016-08-03 hoist.tex
optimistic approach

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.

\subsection{Triangle approach}
This is the most basic approach to code-hoisting when the instructions are
hoisted to immediate parent in a diamond like structure. When there are
identical computations in both the branches of a conditional, and all the
legality checks are met, the instruction can be hoisted to the predecessor basic
block. This approach is simple to implement and has minimal impact on the
register pressure.

@@

@@

\section{Partition the list of hoisting candidates to maximize hoisting}
The set of candidates are sorted in the order of their DFS-in
numbers. So that candidates close to each other in the list are also
closer (??) in the CFG.

>>>>

\section{Comparative analysis of different approaches to hoisting}
\subsection{Triangle approach}
This is the most basic approach to code-hoisting when the instructions are
hoisted to immediate parent in a diamond like structure. When there are
identical computations in both the branches of a conditional, and all the
legality checks are met, the instruction can be hoisted to the predecessor basic
block. This approach is simple to implement and has minimal impact on the
register pressure.

@@

\subsection{Optimistic approach}
In this approach, the goal is to maximise the total number of hoistings in the
entire function.  This algorithm is very useful when optimizing for code-size.
We see a lot of computations hoisted \ref{experimental-results}. In order to do
that, we collect the GVN of all the instructions in the function. After that we
iterate on the list of instructions having identical GVN. After that we find the
common dominator dominating all the identical computations and try to hoist the
instruction in that basic block, if feasible. Many times it is not possible to
hoist all the instructions to one common dominator, due to legality/profitability
constraints. In those cases, the algorithmn would partion the list of computations
a partially hoist a set of computations to their common dominator. For more details
see \ref{sec:partition}

\subsubsection{pros,cons}
Naturally, the amount of hoisting depends on the generality of the GVN
algorithm. Current llvm GVN implementation finds out equivalence between
dependent instructions to some extent.

@@

\section{Partition the list of hoisting candidates to maximize hoisting}
\cite{sec:partition}
The set of candidates are sorted in the order of their DFS-in
numbers. So that candidates close to each other in the list are also
closer (??) in the CFG.
